Project Notes

### 2020-04-23 notes/notes.tex
Notes: update 23/04/2020

>>>>

\paragraph{23/04/2020}
\begin{itemize}
\item
Prove preservation of full-mergeability -- for global types
$G_1, G_2$ and role $r$, if $(G_1 \upharpoonright r)
\sqcap (G_2 \upharpoonright r)$ exists, then the projections 
from the encodings should be mergeable too, i.e. 
($\llbracket G_1, s \rrbracket \upharpoonright r)
\sqcap (\llbracket G_2, s \rrbracket \upharpoonright r)$
exists too.

\item
Implement the TwoBuyer protocol in code -- modified templates
for routing messages in server role.

\item
Identified additional lemmas to prove for full-mergeability;
likewise for the well-formedness proof (found a caveat with
inductive case for proving encoding of recursion, because
the way the encoding handles recursion is different from how
projection handles recursion -- the latter projects depending
on whether the role to project to is a participant).
\end{itemize}
